%=========================
% resume.tex
%=========================
\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{classic}  % style options: 'casual', 'classic', 'oldstyle', 'banking'
\moderncvcolor{blue}     % color options: 'blue', 'orange', 'green', 'red', 'purple', 'grey', 'black'

% Character encoding
\usepackage[utf8]{inputenc}   % if you need to handle special characters
\usepackage[T1]{fontenc}      % better handling of hyphenation

% Adjust the font used by your name and title
\renewcommand*{\namefont}{\fontsize{20}{22}\bfseries}
\renewcommand*{\titlefont}{\fontsize{10}{12}\mdseries}

% Adjust page margins
% \usepackage[scale=0.85]{geometry}
\usepackage[scale=0.9, top=1in, bottom=1in]{geometry}

% Personal info
\name{Kyle}{Jackson}
% \title{Resume} % optional
\address{556 Cultivate}{Irvine, CA 92618} % optional
\phone[mobile]{(608) 334-4154} % optional
\email{kyle@jacksonk.com}  % optional
\homepage{kylejackson.org} % optional
\social[linkedin]{kjackson87}

\begin{document}

%=========================
% CONTACT HEADER
%=========================
\makecvtitle
\vspace{-1em}  % negative space to pull content up

%-----------------------------------
% STEP 2.1: ADD A SUMMARY SECTION
%-----------------------------------
\section{Summary}
\cvitem{}{
  Principal Applied Science Lead specializing in AI safety, LLM evaluation systems, and automated red-teaming solutions.
  Leading Microsoft's efforts in developing sophisticated LLM-based safety evaluations and harm detection systems.
  Proven track record of architecting large-scale AI solutions that combine cutting-edge research with practical
  implementation, including synthetic data generation, automated content evaluation, and IP protection services.
  Experienced in building and leading technical teams to deliver robust AI systems with a focus on responsible
  deployment and risk mitigation.
}

%=========================
% EMPLOYMENT
%=========================
\section{Employment}

\cventry{Mar 2022 -- Current}
        {Principal Applied Science Lead}
        {Microsoft}
        {}
        {}
        {
          \begin{itemize}
            \item Lead a team of 5 research scientists focused on developing and implementing LLM-based safety evaluations and automated red-teaming solutions.
            \item Unified LLM-Judges with conversation simulation to automate harmful content evaluation across Microsoft AI products, reducing the manual review burden.
              \begin{itemize}
                \item Published: \textit{A Framework for Automated Measurement of Responsible AI Harms in Generative AI Applications} (Magooda, Helyar, Jackson, et al., 2023)
              \end{itemize}
            \item Supervised research internship on prompt injection mitigations.
              \begin{itemize}
                \item Published: \textit{Defense against Prompt Injection Attacks via Mixture of Encodings} (Zhang, Sullivan, Jackson, et al., To appear in NAACL 2025)
              \end{itemize}
            \item Tuned and deployed an automated red-teaming "Red" language model, improving detection of potential policy violations in generative outputs.
            \item Optimized and evaluated an LLM-Judge model, refining its ability to accurately assess harmful or disallowed content.
            \item Created a synthetic "seed" dataset for automated red-teaming, providing a transferrable process for discovering harms in generative models.
            \item Engineered a synthetic data generation platform to elicit harmful content from Bing Copilot, proactively identifying potential risks.
            \item Pioneered a system for evaluating harm detection in Bing Copilot by leveraging "LLM-as-a-Judge" and converting Responsible AI (RAI) policies into actionable guidelines.
            \item Architected and deployed an IP protection service utilizing large-scale text analysis to detect potential intellectual property violations in AI-generated content.
            \item Developed a unified metrics data pipeline that ingests plugin, service, and model telemetry for GitHub Copilot, streamlining analytics and accelerating model improvements.
            \item Designed and delivered a BERT-based malware detection model for GitHub Copilot, enhancing real-time threat identification in code suggestions.
          \end{itemize}
        }

\cventry{Oct 2018 -- Mar 2022}
        {Sr Software Engineer}
        {Microsoft}
        {}
        {}
        {
          \begin{itemize}
            \item Enhanced existing services to allow for seamless new cloud rollout in secure and standard clouds.
            \item Enhanced telemetry of compromised Microsoft accounts to evaluate compromise detection sources.
            \item Built a service to protect 500 million LinkedIn accounts from online compromise.
          \end{itemize}
        }

\cventry{May 2016 -- Sept 2018}
        {Sr Software Engineer}
        {Digital Innovation at Providence}
        {}
        {}
        {
          \begin{itemize}
            \item Built a software delivery platform and Kubernetes infrastructure stack, accelerating new project launches and streamlining deployments.
            \item Led an Operational Excellence initiative to reduce on-call pages and MTTR, cultivating a culture of proactive issue resolution.
            \item Spearheaded the development of a Telehealth web app (TypeScript, WebRTC, React, Java microservices) and introduced a code generator to enhance productivity.
          \end{itemize}
        }

\cventry{June 2010 -- May 2016}
        {Principal Software Engineer}
        {Liberty Mutual}
        {}
        {}
        {
          \begin{itemize}
            \item Led the development of a data-driven Smart Home platform to enhance insurance offerings.
            \item Created a centralized logging framework that improved service reliability and integrated legacy mainframe data into modern systems.
          \end{itemize}
        }

\cventry{Sep 2008 -- May 2010}
        {Research Assistant}
        {Marquette University CS Dept}
        {}
        {}
        {
          \begin{itemize}
            \item Worked on a research team to build the XINU operating system for Linksys routers.
          \end{itemize}
        }

%=========================
% SKILLS
%=========================
\section{Skills}
\cvitem{AI/ML}{LLMs, BERT, PyTorch, TensorFlow, Hugging Face, Responsible AI, Red-teaming}
\cvitem{Cloud \& Infrastructure}{Azure, AWS, Docker, Kubernetes, Microservices}
\cvitem{Programming}{Python, C\#, TypeScript, Java, JavaScript, SQL}
\cvitem{Tools \& Frameworks}{Jupyter, Git, CI/CD, REST APIs, Node.js}

%=========================
% EDUCATION
%=========================
\section{Education}
\cventry{Atlanta, GA}{Georgia Institute of Technology}{Master of Science in Computer Science}{}{}{Focus on Machine Learning}
\cventry{Milwaukee, WI}{Marquette University}{Bachelor of Science in Computer Sciences}{}{}{}

\end{document}